The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$

### 2015-05-14 formalwriteup.tex
propositions 3.1-3.3

In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $S_n$ in characteristic $p$ dividing $n$. This problem is an interesting test case for moving results from characteristic $0$ to positive characteristic. Cherednik algebras, originally double affine Hecke algebras, were introduced by Cherednik in 1993; for an introduction to these algebras we refer to \cite{EM}. The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type $A_{n-1}$ (associated to the symmetric group $S_n$). In general new techniques are required to study positive characteristic as opposed to characteristic 0. In this paper we directly connect the characteristic 0 case for the polynomial representation to the positive characteristic case; the irreducible representation of the Cherednik algebra in this case is the quotient of the polynomial representation by an ideal generated by complex residues. In the positive characteristic case, we instead let the generators be the coefficients of formal power series. In particular our argument that this quotient is a complete intersection is directly analogous to the corresponding argument in \cite{CE}, though with additional `error terms' that emerge because we must truncate the power series so that we can define it in positive characteristic. We are able to truncate the power series because we realize the $(n-1)$-dimensional representation $\h$ of $S_n$ as a quotient by the sum of the basis elements rather than as the reflection representation.

While we only consider the case of the symmetric group $S_n$ in this paper, this technique could also be used for the general case of complex reflection groups. %this bit needs revisions

%mention previous results [BEG],[CE],[GGOR]? ask
%deformation of DAHAs introduced by Etingof-Ginzburg in 2001

@@

\subsection{Main results}

@@

Our study is motivated by previous work on the representation theory of the type $A$ rational Cherednik algebra in both characteristic $0$ and $p$.  The type $A$ non-modular case $p \gg n$ was studied in \cite{BFG}, and the maximal ideal of the polynomial representation were given in both modular and non-modular cases in \cite{BC1}.  In the modular case $p \mid n$, for $p = 2$, it was shown in \cite[Theorem 5.1]{L} that the irreducible quotient of the polynomial representation associated to the $n$-dimensional reflection representation is a complete intersection and that the corresponding maximal ideal is generated by $n - 1$ elements of degree $2$ and a single element of degree $4$.  In particular, this implies that the Hilbert series is 
\[
h(t) = (1 + t)^n (1 + t^2).
\]
It was conjectured by C.~Lian in \cite[Conjecture 5.2]{L} that for all $p$ the corresponding irreducible is a complete intersection with maximal ideal having $n - 1$ generators in degree $p$ and a single generator in degree $p^2$.  Our results are consistent with the restriction of Lian's conjecture to the case when $\h$ is restricted to the $(n - 1)$-dimensional quotient.  It would be interesting to extend our work to prove Lian's conjecture in full.  For general $p \mid n$, a subideal of the maximal ideal was computed in \cite[Proposition 6.1]{DS}.

@@

@@

We let $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$. Let $F_a(z)$ for $a=0,\dots,n-1$ be the formal power series in $z$ defined by $F_a(z)=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k\right)$ where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$.

@@

\begin{proposition}\label{prop:ann} Let $f_a=[z^p]F_a(z)$. Then $f_a$ for $a=0,\dots,n-1$ are annihilated by the Dunkl operators. 
\end{proposition}

@@

@@

Let 
F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right).
Note that $F(z)$ is symmetric and $F_a(z)=\frac{F(z)}{1-x_az}$ for all $a$. Then we see that for all $0 \le i < n-1$ we have 

@@

since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. 

@@

We see easily that 
\[
\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.
\]
We now consider $\frac{\partial F}{\partial z}$.
\begin{align*}
\frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\end{align*}
We define 
\[
V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\]
Then we see that 
\[
\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).
\]
From this it follows that
\begin{align*}
\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_0z}\right)\\
&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F(z)\\
&=\frac{V(z)}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_0}{(1-x_0z)^2} F(z)\\
&=\frac{V(z)}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0(z)+\frac{x_0}{1-x_0z} F_0(z).\\
\end{align*}
We now again consider $(D_1-D_0)(F_0)$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_0$ since that is $0$ in characteristic $p$. 
\begin{align*}
(D_1-D_0)(F_0)&=\frac{G_1(z)-G_0(z)}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\sum_{j} \frac{zc}{1-x_jz}F_0\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{zc}{1-x_jz}F_0\right)-nzcF_0\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{z-x_0z^2}{1-x_0z}F_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}F_0+\frac{zc}{1-x_jz}F_0\right)\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\left(\frac{x_0}{1-x_0z}F_0+\left(\sum_{j}- \frac{x_jc}{1-x_jz}F_0\right)\right)\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V(z)}{1-x_0z}\\
&=\frac{G_1(z)-G_0(z)+z^2V(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}.\\
\end{align*}
We consider $z^2V(z)$ and $G_i(z)$ for $i=0,1$. We note that $(g-1)^{p-1}$ divides $V(z)$ and $z(g-1)^{p-1}$ divides $G_i(z)$. Since the sum $\sum_{a=0}^{n-1} x_a$ is $0$, we see that $z^2 \mid g(z)-1$; therefore $z^{2p-2} \mid (g-1)^{p-1}$. Therefore $z^{p+1} \mid z^{2p-1} \mid G_i(z)$ and $z^{p+1} \mid z^{2p} \mid z^2V(z)$. (We note that $z^p \mid z^{2p-2} \mid V(z)$; this will be relevant later.)

Then we see that for $0 \le \ell \le p$ we have
\[
[z^\ell](z^2V(z))=[z^\ell]G_0(z)=[z^\ell]G_1(z)=0.
\]
Then we also have
\[
[z^\ell](G_1(z)-G_0(z)+z^2V(z))=0.
\]
Then $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is $0$ since it is a linear combination of $[z^\ell](G_1(z)-G_0(z)+z^2V(z))$ for $0 \le \ell \le p$, so 
\[
[z^p]\left((D_1-D_0)(F_0)\right)=[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right).
\]
Let $b=[z^{p-1}](F_0)$. We see that $[z^p](-zF_0)=-b$. Then $[z^{p-2}]\left(\frac{\partial F_0}{\partial z}\right)=(p-1)b=-b$, so $[z^p]\left(-z^2\frac{\partial F_0}{\partial z}\right)=b$. Therefore $[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right)=-b+b=0$, so 
\[
[z^p]((D_1-D_0)(F_0))=(D_1-D_0)([z^p]F_0)=(D_1-D_0)f_0=0.
\]
By the symmetry of the $F_a$, this is the only Dunkl operator we need consider; it is clear that all the $f_a$ are killed by the Dunkl operators.
\end{proof}

\begin{proposition}\label{prop:linind} The $f_a$ for $a=0,\dots,n-2$ are linearly independent homogeneous polynomials of degree $p$.
\end{proposition}

\begin{proof} 
We recall that $F_a(z)=\frac{1}{1-x_az}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$. It is then clear that $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$, since $[z^k]F_a(z)$ is a homogeneous polynomial in the $x_i$ of degree $k$ for all $k$ (this follows from the fact that this is true in both multiplicands in $F_a$).

Assume $\sum_{a=0}^{n-2} \lambda_af_a=0$ for some $\lambda_a \in k$. Then in particular this must be true when we set $x_a=1$ and $x_i=0$ for $i \ne a,i < n-1$. (We let $x_{n-1}=-1$ so that $\sum x_i=0$.) Note that if this is the case that $g(z)=(1-z)(1+z)=1-z^2$, so 
\[
F_a(z)=\left(\sum_{k=0}^\infty z^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)
\]
and 
\[
F_i(z)=\left(\sum_{k=0}^\infty 0^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)=\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k
\]
for $n-1>i \ne a$.

Therefore we have $[z^p]F_a(z)=f_a=\sum_{k=0}^{(p-1)/2} (-1)^k\binom{c}{k}=\binom{c-1}{(p-1)/2}$ and $[z^p]F_i(z)=f_i=0$ for $n-1>i \ne a$ (since $p > 2$). Since $c$ is generic, we can assume $\binom{c-1}{(p-1)/2} \ne 0$. Then since $\sum_{a=0}^{n-2} \lambda_af_a=0$, we see that $\lambda_a\binom{c-1}{(p-1)/2}=0$; then we must have $\lambda_a=0$.

By setting $x_a=1,x_{n-1}=-1$ and $x_i=0$ for $i \ne a, i \ne n-1$ for all $a=0,\dots,n-1$ in succession, we find that $\lambda_a=0$ for all $a$. Therefore the $f_a$ for $a=0,\dots,n-2$ are linearly independent as desired.
\end{proof}

\begin{proposition}\label{prop:vand}Let $y_0, \ldots, y_{r - 1}$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - y_j z)$ are linearly independent.
\end{proposition}
\begin{proof} 
Assume that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.  Then $\left(\prod_j (1-y_jz)\right)\left(\sum_i \frac{\lambda_i}{1-y_iz}\right)$ must be $0$ in the ring of formal power series. Therefore since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-y_iz}=0$. Then in particular for $\ell=0,\dots,r-1$ we have $\sum_i \lambda_iy_i^\ell=0$.

This implies that the product of the Vandermonde matrix 
\[
\left(\begin{matrix} 1& 1& \dots& 1\\y_0&y_1&\dots&y_{r-1}\\\dots&\dots&\dots&\dots\\y_0^{r-1}&y_1^{r-1}&\dots&y_{r-1}^{r-1}\end{matrix}\right)
\]
with the column vector $(\lambda_0,\dots,\lambda_{r-1})$ is $0$; however since all the $y_i$ are distinct, the Vandermonde matrix has nonzero determinant $\prod_{0 \le i < j \le r-1} (y_i-y_j)$, implying that $\lambda_i=0$ for all $i$.

@@

\begin{proposition}\label{prop:ci} Let $I \subseteq A$ be the ideal generated by $f_a$ for $a=0,\dots,n-2$. $A/I$ is a complete intersection. 
\end{proposition}

>>>>

The present work presents a detailed study of the polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra over a field of characteristic $p$ dividing $n$.  Rational Cherednik algebras were introduced by Etingof-Ginzburg in \cite{EG} as a rational degeneration of the double affine Hecke algebra dependent on two parameters $\hbar$ and $c$.  In characteristic $0$, their type $A$ representation theory has been the subject of extensive study.  We refer the reader to \cite{EM} for a survey of these results.

In characteristic $p$ and especially in the modular case, much less is known about the representation theory of the rational Cherednik algebra.  In this paper, we consider the modular case $p \mid n$.  For $\hbar = 1$ and generic $c$, we provide a complete characterization of the irreducible quotient of the polynomial representation.  We give explicit generators for the unique maximal ideal, show that the irreducible quotient is a complete intersection, and compute its Hilbert series.

Our techniques are inspired by taking characteristic $p$ analogues of results about Cherednik algebras in characteristic $0$.  In particular, our explicit expression for generators of the maximal ideal was obtained by converting expressions containing complex residues to equivalent expressions dealing only with formal power series which may be interpreted in characteristic $p$.  While we restrict our present study to the polynomial representation in type $A$, we view this problem as a test case for this philosophy and believe it may admit wider application.

In the remainder of this introduction, we give precise statements of our results and explain how they relate to other recent work.

@@

\subsection{Statement of the main results}

@@

Our study is motivated by previous work on the representation theory of the type $A$ rational Cherednik algebra in both characteristic $0$ and $p$.  The type $A$ non-modular case $p \gg n$ was studied in \cite{BFG}, and the maximal ideal of the polynomial representation were given in both modular and non-modular cases in \cite{BC1}.  In the modular case $p \mid n$, for $p = 2$, it was shown in \cite[Theorem 5.1]{L} that the irreducible quotient of the polynomial representation associated to the $n$-dimensional reflection representation is a complete intersection and that the corresponding maximal ideal is generated by $n - 1$ elements of degree $2$ and a single element of degree $4$.  In particular, this implies that the Hilbert series is 
\[
h(t) = (1 + t)^n (1 + t^2).
\]
It was conjectured by Lian in \cite[Conjecture 5.2]{L} that for all $p$ the corresponding irreducible is a complete intersection with maximal ideal having $n - 1$ generators in degree $p$ and a single generator in degree $p^2$.  Our results are consistent with the restriction of Lian's conjecture to the case when $\h$ is restricted to the $(n - 1)$-dimensional quotient.  It would be interesting to extend our work to prove Lian's conjecture in full.  For general $p \mid n$, a subideal of the maximal ideal was computed in \cite[Proposition 6.1]{DS}.

@@

\subsection{Outline of the paper}

The remainder of this paper is organized as follows.  In Section 2, we give some necessary background on rational Cherednik algebras and fix the form of the Dunkl operators which will be used in later computations.  In Section 3, we check that our generators are singular vectors, show that they cut out a complete intersection, and finally deduce Theorem \ref{thm:main}.

@@

\subsection{An explicit construction of singular vectors}

We let $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$ and $F(z)$ be the formal power series in $z$ defined by
\[
F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right).
\]
where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$. 
Let $F_i(z)$ for $i=0,\dots,n-1$ be $\frac{F(z)}{1-x_iz}$ and $f_i=[z^p]F_i(z)$. The $f_i$ will be the generators of the maximal ideal $J$.

@@

\begin{proposition}\label{prop:ann} The elements $f_i$ for $i=0,\dots,n-1$ are annihilated by $D_i-D_j$ for all $i \ne j$.
\end{proposition}

@@

We see that for all $i$, $f_i$ is symmetric in the $x_j$ for $j \ne i$. It therefore suffices to consider the action of the Dunkl operators on $f_0$. We note that the Dunkl operators $D_i-D_j$ for all $i \ne j$ are spanned by $D_i-D_0$ for $0<i \le n-1$; then because $f_0$ is symmetric in the $x_i$ with $i > 0$, we see that it suffices to consider the action of $D_1-D_0$ on $f_0$ to show that the $f_i$ are annihilated by $D_i \ne D_j$ for all $i \ne j$.

@@

We recall that $F(z)$ is symmetric and $F_a(z)=\frac{F(z)}{1-x_az}$ for all $a$. Then we see that for all $0 \le i < n-1$ we have 

@@

since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. We now compute

@@

We see easily that 
\[
\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.
\]
We now consider $\frac{\partial F}{\partial z}$. We compute
\begin{align*}
\frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\end{align*}
We define 
\[
V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\]
Then we see that 
\[
\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).
\]
From this it follows that
\begin{align*}
\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_0z}\right)\\
&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F(z)\\
&=\frac{V(z)}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_0}{(1-x_0z)^2} F(z)\\
&=\frac{V(z)}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0(z)+\frac{x_0}{1-x_0z} F_0(z).\\
\end{align*}
We now again consider $(D_1-D_0)(F_0)$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_0$ since that is $0$ in characteristic $p$. 
\begin{align*}
(D_1-D_0)(F_0)&=\frac{G_1(z)-G_0(z)}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\sum_{j} \frac{zc}{1-x_jz}F_0\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{zc}{1-x_jz}F_0\right)-nzcF_0\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{z-x_0z^2}{1-x_0z}F_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}F_0+\frac{zc}{1-x_jz}F_0\right)\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\left(\frac{x_0}{1-x_0z}F_0+\left(\sum_{j}- \frac{x_jc}{1-x_jz}F_0\right)\right)\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V(z)}{1-x_0z}\\
&=\frac{G_1(z)-G_0(z)+z^2V(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}.\\
\end{align*}
We consider $z^2V(z)$ and $G_i(z)$ for $i=0,1$. We note that $(g-1)^{p-1}$ divides $V(z)$ and $z(g-1)^{p-1}$ divides $G_i(z)$. Since the sum $\sum_{a=0}^{n-1} x_a$ is $0$, we see that $z^2 \mid g(z)-1$; therefore $z^{2p-2} \mid (g-1)^{p-1}$. Therefore $z^{p+1} \mid z^{2p-1} \mid G_i(z)$ and $z^{p+1} \mid z^{2p} \mid z^2V(z)$. (We note that $z^p \mid z^{2p-2} \mid V(z)$; this will be relevant later.)

Then we see that for $0 \le \ell \le p$ we have
\[
[z^\ell](z^2V(z))=[z^\ell]G_0(z)=[z^\ell]G_1(z)=0.
\]
Then we also have
\[
[z^\ell](G_1(z)-G_0(z)+z^2V(z))=0.
\]
Then $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is $0$ since it is a linear combination of $[z^\ell](G_1(z)-G_0(z)+z^2V(z))$ for $0 \le \ell \le p$, so 
\[
[z^p]\left((D_1-D_0)(F_0)\right)=[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right).
\]
Let $b=[z^{p-1}](F_0)$. We see that $[z^p](-zF_0)=-b$. Then $[z^{p-2}]\left(\frac{\partial F_0}{\partial z}\right)=(p-1)b=-b$, so $[z^p]\left(-z^2\frac{\partial F_0}{\partial z}\right)=b$. Therefore $[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right)=-b+b=0$, so 
\[
[z^p]((D_1-D_0)(F_0))=(D_1-D_0)([z^p]F_0)=(D_1-D_0)f_0=0.
\]
By the symmetry of the $F_i$, this is the only Dunkl operator we need consider; it is clear that all the $f_i$ are killed by the Dunkl operators.
\end{proof}

\begin{proposition}\label{prop:linind} The $f_i$ for $i=0,\dots,n-2$ are linearly independent homogeneous polynomials of degree $p$.
\end{proposition}

\begin{proof} 
We recall that $F_i(z)=\frac{1}{1-x_iz}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)=\left(\sum_{k=0}^\infty x_i^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$. It is then clear that $f_i$ is a homogeneous polynomial in the $x_j$ of degree $p$, since $[z^k]F_i(z)$ is a homogeneous polynomial in the $x_j$ of degree $k$ for all $k$ (this follows from the fact that this is true in both multiplicands in $F_i$).

Assume $\sum_{i=0}^{n-2} \lambda_if_i=0$ for some $\lambda_i \in k$. Then in particular this must be true when we set $x_j=1$ and $x_i=0$ for $i \ne j,i < n-1$. (We let $x_{n-1}=-1$ so that $\sum x_i=0$.) Note that if this is the case that $g(z)=(1-z)(1+z)=1-z^2$, so 
\[
F_j(z)=\left(\sum_{k=0}^\infty z^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)
\]
and 
\[
F_i(z)=\left(\sum_{k=0}^\infty 0^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)=\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k
\]
for $n-1>i \ne j$.

Therefore we have $[z^p]F_j(z)=f_j=\sum_{k=0}^{(p-1)/2} (-1)^k\binom{c}{k}=\binom{c-1}{(p-1)/2}$ and $[z^p]F_i(z)=f_i=0$ for $n-1>i \ne j$ (since $p > 2$). Since $c$ is generic, we can assume $\binom{c-1}{(p-1)/2} \ne 0$. Then since $\sum_{i=0}^{n-2} \lambda_if_i=0$, we see that $\lambda_j\binom{c-1}{(p-1)/2}=0$; then we must have $\lambda_j=0$.

By setting $x_j=1,x_{n-1}=-1$ and $x_i=0$ for $i \ne j, i \ne n-1$ for all $j=0,\dots,n-1$ in succession, we find that $\lambda_j=0$ for all $j$. Therefore the $f_i$ for $i=0,\dots,n-2$ are linearly independent as desired.
\end{proof}

\subsection{Complete interesction properties}

\begin{proposition}\label{prop:vand}Let $y_0, \ldots, y_{r - 1}$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - y_j z)$ are linearly independent.
\end{proposition}
\begin{proof} 
Suppose that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.  Then $\left(\prod_j (1-y_jz)\right)\left(\sum_i \frac{\lambda_i}{1-y_iz}\right)$ must be $0$ in the ring of formal power series. Since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-y_iz}=0$. In particular for $\ell=0,\dots,r-1$ we have $\sum_i \lambda_iy_i^\ell=0$.

However, the vectors $(1,y_i,\dots,y_i^{r-1})$ are linearly independent by the Vandermonde determinant, so $\lambda_i=0$ for all $i$.

@@

\begin{proposition}\label{prop:ci} Let $I \subseteq A$ be the ideal generated by $f_i$ for $i=0,\dots,n-2$.  The $A/I$ is a complete intersection. 
\end{proposition}
